\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-10-02 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
fixing vignettes
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@70084 bc3139a8-67e5-0310-9ffc-ced21a209358

<<knitr, include=FALSE, cache=FALSE>>=
library(knitr)
opts_chunk$set(fig.align = 'center', 
               fig.show = 'hold', 
               par = TRUE,
               prompt = TRUE,
               comment = NA)
options(replace.assign = TRUE, 
        width = 68)
knit_hooks$set(par = function(before, options, envir) {
  if (before && options$fig.show != 'none') 
    par(mar = c(4,4,.1,.1),
        cex.lab = .95,
        cex.axis = .9,
        mgp = c(2,.7,0),
        tcl = -.3)
})
@

>>>>

<<knitr, include=FALSE, cache=FALSE>>=
library(knitr)
opts_chunk$set(fig.align = 'center', 
               fig.show = 'hold', 
               par = TRUE,
               prompt = TRUE,
               comment = NA)
options(replace.assign = TRUE, 
        width = 68)
## knit_hooks$set(par = function(before, options, envir) {
##   if (before && options$fig.show != 'none') 
##     par(mar = c(4,4,.1,.1),
##         cex.lab = .95,
##         cex.axis = .9,
##         mgp = c(2,.7,0),
##         tcl = -.3)
## })
@
